% custom-template.tex

\documentclass[11pt,]{article}

% Add additional LaTeX packages if needed

\usepackage[colorlinks]{hyperref}


% Define the appearance of level 2 headings

% Custom formatting for level 2 headings
\makeatletter
\renewcommand\subsection{\@startsection{subsection}{2}{\z@}
  {-2ex \@plus -1ex \@minus -.2ex}
  {1.5ex \@plus .2ex}
  {\normalfont\bfseries\HUGE}}
  % Adjust the font size and style here
\makeatother

%\titleformat{\subsection}[block]{\normalfont\large\bfseries\scshape}{\thesubsection}{1em}{}

\begin{document}
\hypertarget{education}{%
\section{Education}\label{education}}

\hypertarget{university-of-michigan}{%
\subsubsection{University of Michigan}\label{university-of-michigan}}

Postdoctoral Research Fellow, Department of Internal Medicine (NIH T32
training grant)\\
Postdoctoral Research Fellow, Department of Biostatistics

\hypertarget{university-of-massachusetts-medical-school}{%
\subsubsection{University of Massachusetts Medical
School}\label{university-of-massachusetts-medical-school}}

Postdoctoral Research Fellow, Department of Microbiology \&
Physiological Systems

\hypertarget{university-of-wisconsin-madison}{%
\subsubsection{University of
Wisconsin-Madison}\label{university-of-wisconsin-madison}}

Postdoctoral Research Fellow, Department of Biostatistics and Medical
Informatics\\
Ph.D., Department of Statistics\\
Postdoctoral Research Fellow, Molecular and Environmental Toxicology
Center\\
Assistant Researcher, Value-Added Research Center

\hypertarget{university-of-washington}{%
\subsubsection{University of
Washington}\label{university-of-washington}}

Postdoctoral Research Fellow, Department of Biostatistics

\hypertarget{university-of-wisconsin-madison-1}{%
\subsubsection{University of
Wisconsin-Madison}\label{university-of-wisconsin-madison-1}}

M.D., School of Medicine and Public Health\\
M.S., Department of Population Health Sciences\\
B.S., with Honors in Chemistry, Mathematics, and Biochemistry, College
of Letters and Science

Ann Arbor, Michigan, USA\\
2023 to present\\
2021 to 2023

Worcester, Massachusetts, USA\\
2019 to 2021

Madison, Wisconsin, USA\\
2019\\
2011 to 2019\\
2012 to 2014\\
2011

Seattle, Washington, USA\\
2007 to 2009

Madison, Wisconsin, USA\\
2003 to 2007\\
2003 to 2007\\
1996 to 2001

\hypertarget{submitted-manuscripts}{%
\section{Submitted Manuscripts}\label{submitted-manuscripts}}

\hypertarget{refs-submitted}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-kurtz2024}{}}%
\textsc{Kurtz}, Sherry L., Richard \textsc{Baker}, Frederick
\textsc{Boehm}, Chelsea \textsc{Lehman}, Lara \textsc{Mittereder}, Hamda
\textsc{Khan}, Amy \textsc{Rossi}, et al. Presented at the Multiple
genetic loci influence vaccine-induced protection against mycobacterium
tuberculosis in genetically diverse mice, n.d.

\end{CSLReferences}

\hypertarget{journal-articles}{%
\section{Journal Articles}\label{journal-articles}}

\hypertarget{refs-peer}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-boehm2022statistical}{}}%
\textsc{Boehm}, Frederick J, and Xiang \textsc{Zhou}. {``Statistical
Methods for Mendelian Randomization in Genome-Wide Association Studies:
A Review.''} \emph{Computational and Structural Biotechnology Journal},
2022.

\leavevmode\vadjust pre{\hypertarget{ref-smith2022host}{}}%
\textsc{Smith}, Clare M, Richard E \textsc{Baker}, Megan K
\textsc{Proulx}, Bibhuti B \textsc{Mishra}, Jarukit E \textsc{Long}, Sae
Woong \textsc{Park}, Ha-Na \textsc{Lee}, et al. {``Host-Pathogen Genetic
Interactions Underlie Tuberculosis Susceptibility in Genetically Diverse
Mice.''} \emph{Elife} 11 (2022): e74419.

\leavevmode\vadjust pre{\hypertarget{ref-boehm2020happening}{}}%
\textsc{Boehm}, Frederick J, and Bret M \textsc{Hanlon}. {``What Is
Happening on Twitter? A Framework for Student Research Projects with
Tweets.''} \emph{Journal of Statistics and Data Science Education},
2021, S95--102. \url{https://doi.org/10.1080/10691898.2020.1848486}.

\leavevmode\vadjust pre{\hypertarget{ref-rodriguez2020genetic}{}}%
\textsc{Rodriguez-Gil}, Jorge L, Dawn E \textsc{Watkins-Chow}, Laura L
\textsc{Baxter}, Gene \textsc{Elliot}, Ursula L \textsc{Harper}, Stephen
M \textsc{Wincovitch}, Julia C \textsc{Wedel}, et al. {``Genetic
Background Modifies Phenotypic Severity and Longevity in a Mouse Model
of Niemann-Pick Disease Type C1.''} \emph{Disease Models\\
\& Mechanisms} 13, no. 3 (2020).

\leavevmode\vadjust pre{\hypertarget{ref-boehm2018test}{}}%
\textsc{Boehm}, Frederick J., Elissa J. \textsc{Chesler}, Brian S.
\textsc{Yandell}, and Karl W. \textsc{Broman}. {``Testing Pleiotropy Vs.
Separate QTL in Multiparental Populations.''} \emph{G3}, 2019.
\url{https://doi.org/10.1534/g3.119.400098}.

\leavevmode\vadjust pre{\hypertarget{ref-boehm2019qtl2pleio}{}}%
\textsc{Boehm}, Frederick, Brian \textsc{Yandell}, and Karl W
\textsc{Broman}. {``Qtl2pleio: Testing Pleiotropy Vs. Separate QTL in
Multiparental Populations.''} \emph{Journal of Open Source Software} 4,
no. 38 (2019): 1435. \url{https://doi.org/10.21105/joss.01435}.

\leavevmode\vadjust pre{\hypertarget{ref-kemis2019genetic}{}}%
\textsc{Kemis}, Julia H, Vanessa \textsc{Linke}, Kelsey L
\textsc{Barrett}, Frederick J \textsc{Boehm}, Lindsay L
\textsc{Traeger}, Mark P \textsc{Keller}, Mary E \textsc{Rabaglia}, et
al. {``Genetic Determinants of Gut Microbiota Composition and Bile Acid
Profiles in Mice.''} \emph{PLoS Genetics} 15, no. 8 (2019): e1008073.

\leavevmode\vadjust pre{\hypertarget{ref-wells2016how}{}}%
\textsc{Wells}, Chris, Dhavan V. \textsc{Shah}, Jon C.
\textsc{Pevehouse}, JungHwan \textsc{Yang}, Ayellet \textsc{Pelled},
Frederick \textsc{Boehm}, Josephine \textsc{Lukito}, Shreenita
\textsc{Ghosh}, and Jessica L. \textsc{Schmidt}. {``How Trump Drove
Coverage to the Nomination: Hybrid Media Campaigning.''} \emph{Political
Communication} 33, no. 4 (2016): 669--76.
\url{https://doi.org/10.1080/10584609.2016.1224416}.

\leavevmode\vadjust pre{\hypertarget{ref-tauchman2015stable}{}}%
\textsc{Tauchman}, Eric C, Frederick J \textsc{Boehm}, and Jennifer G
\textsc{DeLuca}. {``Stable Kinetochore-Microtubule Attachment Is
Sufficient to Silence the Spindle Assembly Checkpoint in Human Cells.''}
\emph{Nature Communications} 6 (2015).

\leavevmode\vadjust pre{\hypertarget{ref-costello2014community}{}}%
\textsc{Costello}, James C, Laura M \textsc{Heiser}, Elisabeth
\textsc{Georgii}, Mehmet \textsc{Gönen}, Michael P \textsc{Menden},
Nicholas J \textsc{Wang}, Mukesh \textsc{Bansal}, et al. {``A Community
Effort to Assess and Improve Drug Sensitivity Prediction Algorithms.''}
\emph{Nature Biotechnology} 32, no. 12 (2014): 1202--12.

\leavevmode\vadjust pre{\hypertarget{ref-dove2014strategy}{}}%
\textsc{Dove}, William F, Alexandra \textsc{Shedlovsky}, Linda
\textsc{Clipson}, James M \textsc{Amos-Landgraf}, Richard B
\textsc{Halberg}, Kathleen J \textsc{Krentz}, Frederick J
\textsc{Boehm}, Michael A \textsc{Newton}, David J \textsc{Adams}, and
Thomas M \textsc{Keane}. {``A Strategy to Identify Dominant Point Mutant
Modifiers of a Quantitative Trait.''} \emph{G3: Genes\textbar{}
Genomes\textbar{} Genetics} 4, no. 6 (2014): 1113--21.

\leavevmode\vadjust pre{\hypertarget{ref-fawzi2010economic}{}}%
\textsc{Fawzi}, MC Smith, W \textsc{Lambert}, F \textsc{Boehm}, JL
\textsc{Finkelstein}, JM \textsc{Singler}, F \textsc{Léandre}, P
\textsc{Nevil}, et al. {``Economic Risk Factors for HIV Infection Among
Women in Rural Haiti: Implications for HIV Prevention Policies and
Programs in Resource-Poor Settings.''} \emph{Journal of Women's Health}
19, no. 5 (2010): 885--92.

\leavevmode\vadjust pre{\hypertarget{ref-laurie2010quality}{}}%
\textsc{Laurie}, Cathy C, Kimberly F \textsc{Doheny}, Daniel B
\textsc{Mirel}, Elizabeth W \textsc{Pugh}, Laura J \textsc{Bierut},
Tushar \textsc{Bhangale}, Frederick \textsc{Boehm}, et al. {``Quality
Control and Quality Assurance in Genotypic Data for Genome-Wide
Association Studies.''} \emph{Genetic Epidemiology} 34, no. 6 (2010):
591--602.

\leavevmode\vadjust pre{\hypertarget{ref-gestwicki2002cell}{}}%
\textsc{Gestwicki}, Jason E, Laura E \textsc{Strong}, Christopher W
\textsc{Cairo}, Frederick J \textsc{Boehm}, and Laura L
\textsc{Kiessling}. {``Cell Aggregation by Scaffolded Receptor
Clusters.''} \emph{Chemistry\\
\& Biology} 9, no. 2 (2002): 163--69.

\end{CSLReferences}

\hypertarget{book}{%
\section{Book}\label{book}}

\hypertarget{refs-book}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-moorthy2009pathophysiology}{}}%
\textsc{Moorthy}, A Vishnu, Bryan Neil \textsc{Becker}, Frederick J
\textsc{Boehm III}, and Arjang \textsc{Djamali}. \emph{Pathophysiology
of Kidney Disease and Hypertension}. Saunders/Elsevier, 2009.

\end{CSLReferences}

\hypertarget{book-chapters}{%
\section{Book Chapters}\label{book-chapters}}

\hypertarget{refs-collection}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-pelled2018}{}}%
\textsc{Pelled}, Ayellet, Josephine \textsc{Lukito}, Frederick
\textsc{Boehm}, JungHwan \textsc{Yang}, and Dhavan \textsc{Shah}.
{``{`Little Marco,'} {`Lyin' Ted,'} {`Crooked Hillary,'} and the
{`Biased'} Media: How Trump Used Twitter to Attack and Organize.''} In
\emph{Digital Discussions: How Big Data Informs Political
Communication}, edited by Natalie \textsc{Stroud} and Shannon
\textsc{McGregor}, 176--96. Routledge, 2018.

\leavevmode\vadjust pre{\hypertarget{ref-boehm2009metabolic}{}}%
\textsc{Boehm}, Frederick, Kelly \textsc{Traeger}, and Arjang
\textsc{Djamali}. {``Metabolic Acidosis and Approach to Acid-Base
Disorders.''} In \emph{Pathophysiology of Kidney Disease and
Hypertension}, edited by Vishnu \textsc{Moorthy}, Bryan \textsc{Becker},
Frederick \textsc{Boehm}, and Arjang \textsc{Djamali}, 79--88.
Saunders/Elsevier, 2009.

\leavevmode\vadjust pre{\hypertarget{ref-moorthy2009urinalysis}{}}%
\textsc{Moorthy}, Vishnu, and Frederick \textsc{Boehm}. {``Urinalysis
and an Approach to Kidney Diseases.''} In \emph{Pathophysiology of
Kidney Disease and Hypertension}, edited by Vishnu \textsc{Moorthy},
Bryan \textsc{Becker}, Frederick \textsc{Boehm}, and Arjang
\textsc{Djamali}, 121--30. Saunders/Elsevier, 2009.

\leavevmode\vadjust pre{\hypertarget{ref-traeger2009acid}{}}%
\textsc{Traeger}, Kelly, Frederick \textsc{Boehm}, and Arjang
\textsc{Djamali}. {``Acid-Base Homeostasis and Metabolic Alkalosis.''}
In \emph{Pathophysiology of Kidney Disease and Hypertension}, edited by
Vishnu \textsc{Moorthy}, Bryan \textsc{Becker}, Frederick
\textsc{Boehm}, and Arjang \textsc{Djamali}, 63--78. Saunders/Elsevier,
2009.

\end{CSLReferences}

\hypertarget{software}{%
\section{Software}\label{software}}

\hypertarget{refs-software}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-qtl2pleio}{}}%
\textsc{Boehm}, Frederick. {``Qtl2pleio {R} Package,''} June 4, 2018.
\url{https://github.com/fboehm/qtl2pleio}.

\leavevmode\vadjust pre{\hypertarget{ref-gemma2}{}}%
---------. {``Gemma2 {R} Package,''} March 15, 2018.
\url{https://github.com/fboehm/gemma2}.

\end{CSLReferences}

\hypertarget{conference-proceedings}{%
\section{Conference Proceedings}\label{conference-proceedings}}

\hypertarget{refs-proceedings}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-mark2011p2}{}}%
\textsc{Mark}, J, L \textsc{Wesler}, C \textsc{Oswald}, F
\textsc{Léandre}, P \textsc{Nevil}, D \textsc{Bertrand}, J
\textsc{Bertrand}, F \textsc{Boehm}, and MC Smith \textsc{Fawzi}.
{``P2-S9. 07 Economic Risk Factors for Syphilis Infection Among Pregnant
Women in Rural Haiti.''} In \emph{Sexually Transmitted Infections},
87:A263--63. Suppl 1. BMJ Publishing Group Ltd, 2011.

\leavevmode\vadjust pre{\hypertarget{ref-marchani2009contrasting}{}}%
\textsc{Marchani}, Elizabeth E, Yanming \textsc{Di}, Yoonha
\textsc{Choi}, Charles \textsc{Cheung}, Ming \textsc{Su}, Frederick
\textsc{Boehm}, Elizabeth A \textsc{Thompson}, and Ellen M
\textsc{Wijsman}. {``Contrasting Identity-by-Descent Estimators,
Association Studies, and Linkage Analyses Using the Framingham Heart
Study Data.''} In \emph{BMC Proceedings}, 3:S102. Suppl 7. BioMed
Central Ltd, 2009.

\leavevmode\vadjust pre{\hypertarget{ref-gestwicki2001mechanistic}{}}%
\textsc{Gestwicki}, JE, CW \textsc{Cairo}, FJ \textsc{Boehm}, and LL
\textsc{Kiessling}. {``Mechanistic Origins of the Valency Effect:
Multivalent Ligand Binding Studied by Surface Plasmon Resonance and
Isothermal Titration Calorimetry.''} In \emph{ABSTRACTS OF PAPERS OF THE
AMERICAN CHEMICAL SOCIETY}, 221:U56--56. American Chemical Society,
2001.

\leavevmode\vadjust pre{\hypertarget{ref-fasella2000synthesis}{}}%
\textsc{Fasella}, E, FJ \textsc{Boehm}, and LL \textsc{Kiessling}.
{``Synthesis of Galactosyl-Alpha (1-3)-Galactosyl Epitopes for Use in
Immunological Studies.''} In \emph{ABSTRACTS OF PAPERS OF THE AMERICAN
CHEMICAL SOCIETY}, 219:U108--8. American Chemical Society, 2000.

\end{CSLReferences}

\hypertarget{other-publications}{%
\section{Other Publications}\label{other-publications}}

\hypertarget{refs-misc}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-derose2014victorian}{}}%
\textsc{DeRose}, Catherine, Carrie \textsc{Roy}, and Fred
\textsc{Boehm}. {``Victorian Eyes: Literary, Statistical, and Artistic
Perspectives on Victorian Novels -- and Dickens's Unfinished Murder
Mystery.''} \emph{Significance}. The Royal Statistical Society, 2014.

\leavevmode\vadjust pre{\hypertarget{ref-boehm1997lone}{}}%
\textsc{Boehm}, Fred. {``The Lone Male Wolf of the Sandhill Wildlife
Area.''} \emph{International Wolf}, 1997.

\end{CSLReferences}

\hypertarget{teaching-experience}{%
\section{Teaching Experience}\label{teaching-experience}}

\hypertarget{formal-courses}{%
\subsection{Formal Courses}\label{formal-courses}}

The College Classroom: Teaching Inclusively Title: Instructor Term: Fall
2017 Institution: CIRTL Network Course: The College Classroom: How to
teach inclusively for educating a diverse nation Title: Co-facilitator
Term: Spring 2017 Institution: University of Wisconsin-Madison Course:
Statistics 371: Introductory statistics for biologists Title: Lecturer
student assistant (Instructor of record) Term: Fall 2016 Institution:
University of Wisconsin-Madison Course: Statistics 679: Data science
Title: Guest lecturer on topic models Term: Fall 2016 Institution:
University of Wisconsin-Madison Course: Statistics 679: Data science
Title: Teaching assistant Term: Fall 2016 Institution: University of
Wisconsin-Madison Course: Statistics 224 \& 324: Introductory statistics
for engineers Title: Lecturer student assistant (Instructor of record)
Term: Spring 2014, Fall 2014, Spring 2015, Fall 2015, Spring 2016
Institution: University of Wisconsin-Madison Course: Statistics 301 \&
371: Introductory statistics Title: Lecturer student assistant
(Instructor of record) Term: Summer 2015 Institution: University of
Wisconsin-Madison Course: Biostatistics 518: Introduction to
biostatistics Title: Teaching assistant Frederick Boehm 6 Term: Winter
2010 Institution: University of Washington Course: Biostatistics 517:
Introduction to biostatistics Title: Teaching assistant Term: Fall 2009
Institution: University of Washington Course: Biostatistics 511 Title:
Teaching assistant Term: Summer 2008 Institution: University of
Washington Course: Chemistry 3B: Introductory organic chemistry Title:
Graduate student instructor Term: Fall 2001 Institution: University of
California-Berkeley

\hypertarget{short-courses-workshops}{%
\subsection{Short Courses \& Workshops}\label{short-courses-workshops}}

Engaging students in the teaching of statistics (twice) Title:
Instructor Dates: July 2020 to August 2020 \& March 2018 to April 2018
Institution: Center for the Integration of Research, Teaching and
Learning Network (https://cirtl.net/)

Short Course: Data analysis with topic models for communications
researchers (twice) Title: Instructor Dates: October 2016 \& July 2016\\
Institution: University of Wisconsin-Madison

Data Carpentry Workshop (twice) Title: Instructor Dates: June 19-20,
2017 (Madison, Wisconsin) \& Sept 15-16, 2018 (Rolla, Missouri)\\
Website: https://uw-madison-aci.github.io/2017-06-19-uwmadison-dc/

Short course: Topic modeling for non-statisticians Title: Instructor
Dates: October 2013 Institution: University of Wisconsin-Madison

Short course: Statistical computing with R Title: Instructor Dates: June
\& July 2013; June \& July 2012 Institution: University of
Wisconsin-Madison

\hypertarget{training-in-teaching}{%
\subsection{Training in Teaching}\label{training-in-teaching}}

\hypertarget{mentoring-experience}{%
\section{Mentoring Experience}\label{mentoring-experience}}

Research mentor to Robert Turner, Undergraduate researcher\\
Project: Topic Modeling of Tweets to Detect Events\\
Dates: May 2015 to May 2016\\
Next position: Software Engineer at Epic Systems

Research mentor to Jinyu Xia, Undergraduate researcher\\
Project: Tweet Sentiments Associate with Stock Market Trends\\
Dates: September 2015 to August 2016\\
Next Position: Graduate student at University of Washington (Department
of Statistics)

\hypertarget{awards-honors}{%
\section{Awards \& Honors}\label{awards-honors}}

\hypertarget{talks-and-presentations}{%
\section{Talks and Presentations}\label{talks-and-presentations}}

\hypertarget{service}{%
\section{Service}\label{service}}

\hypertarget{university-service}{%
\subsection{University Service}\label{university-service}}

\hypertarget{community-service}{%
\subsection{Community Service}\label{community-service}}

\hypertarget{professional-service}{%
\subsection{Professional Service}\label{professional-service}}
\end{document}
